Figures to insert in text

### 2018-03-09 Chapters/Chapter02.tex

>>>>

Kernel comparisons

iMac 1000 bits
Loops	Total time	Scans per second	Time per scan (ms)
single_scan0	3000	15.028241872787476	199.62414934459346	5.009413957595825
single_scan1	3000	11.874222040176392	252.6481305343213	3.958074013392131
single_scan2	3000	13.736932039260864	218.38937482007222	4.578977346420288
single_scan3	3000	11.063963174819946	271.1505771121497	3.687987724939982
single_scan4	3000	12.131728887557983	247.2854469305467	4.043909629185994
single_scan5	3000	11.181737899780273	268.29460920014515	3.7272459665934243
single_scan5_unroll	3000	10.841995000839233	276.7018431356759	3.6139983336130777
single_scan6	3000	12.084025859832764	248.26163356468672	4.028008619944255

iMac 256 bits
Loops	Total time	Scans per second	Time per scan (ms)
single_scan0	3000	9.098679065704346	329.7181907764943	3.0328930219014483
single_scan1	3000	8.634926080703735	347.4262514770137	2.8783086935679116
single_scan2	3000	11.461902141571045	261.7366614149787	3.8206340471903486
single_scan3	3000	11.187175273895264	268.1642082608964	3.729058424631755
single_scan4	3000	13.442016124725342	223.18080652215394	4.480672041575114
single_scan5	3000	11.295457601547241	265.59348950936374	3.76515253384908
single_scan5_unroll	3000	11.396361827850342	263.24190520773243	3.798787275950114
single_scan6	3000	13.104900121688843	228.92200414675017	4.368300040562947

iMac 10k bits
Loops	Total time	Scans per second	Time per scan (ms)
single_scan0	500	30.534967184066772	16.374669636484867	61.069934368133545
single_scan1	500	22.480546236038208	22.24145244293299	44.961092472076416
single_scan2	500	22.491918802261353	22.23020651976254	44.983837604522705
single_scan3	500	6.335015773773193	78.92640174156905	12.670031547546387
single_scan4	500	5.727261781692505	87.30175414685539	11.45452356338501
single_scan5	500	6.294461011886597	79.43491890025042	12.588922023773193
single_scan5_unroll	500	5.688975811004639	87.88928211521136	11.377951622009277
single_scan6	500	5.48170280456543	91.21253337258189	10.96340560913086
